Analysis of Physical Activity Survey(2022)

### 2022-04-27 outputs/paper/paper.Rmd
implemented model code, results section almost complete, introduction almost complete

```{r model, echo = FALSE, fig.pos = 'H'}

```
# Results {#Results}

  From Figure \@ref(fig:fig1) we see a chart comparing the proportion of respondents who were obese based on the different states in the country. From this table we see that the vast majority of residents from both populations receive their water via a pipe directly into their residence. This is a positive as it means these people have quick and direct access to a water source.

```{r fig1, echo = FALSE, fig.cap = "Bar plot of Obesity by State"}
### Bar plot of Obesity by State ###
df1 <- subset(df, Year == 2011)
df2 <- subset(df, Year == 2020)
df1 <- subset(df1, Question == "Percent of adults aged 18 years and older who have obesity")
df1 <- df1[order(df1$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df1[i,4],df1[i+1,4],df1[i+2,4],df1[i+3,4],df1[i+4,4],df1[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df_means <- cbind(unique(df1$Year),unique(df1$State), unique(df1$Question), round(x, digits = 1))
df_means <- as.data.frame(df_means)
df_long <- melt(df_means)
p <- ggplot(df_long, aes(x = V2, y = V4)) + geom_bar(stat = "identity", position = "dodge") +
  xlab("State") +
  ylab("Percent of Population")

p + coord_flip()
```
# Discussion {#Discussion}

>>>>

# Results {#Results}

  From Figure \@ref(fig:fig1) we see a chart comparing the proportion of respondents who were obese based on the different states in the country. We can see from the chart that all states lie between a rate of 20% and 35% obese. The chart below is for 2011

```{r fig1, echo = FALSE, fig.cap = "Bar plot of Obesity by State", fig.width=8,fig.height=8}
### Bar plot of Obesity by State ###
df1 <- subset(df, Year == 2011)
df1 <- subset(df1, Question == "Percent of adults aged 18 years and older who have obesity")
df1 <- df1[order(df1$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df1[i,4],df1[i+1,4],df1[i+2,4],df1[i+3,4],df1[i+4,4],df1[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df_means <- cbind(unique(df1$Year),unique(df1$State), unique(df1$Question), round(x, digits = 1))
df_means <- as.data.frame(df_means)
df_long <- melt(df_means[order(df_means$V4),])
p <- ggplot(df_long, aes(x = V2, y = as.numeric(V4), fill = V4)) +scale_y_continuous(limits = c(0,35)) + theme(legend.position="none", axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=0)) + geom_bar(width = 0.8, stat = "identity", position = 'dodge') +
  xlab("State") +
  ylab("Percent of Population")

p + coord_flip()
```

Below Table \@ref(tab:tab2), shows the states with the lowest proportions of obesity.

```{r tab2, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means2 <- df_means[order(df_means$V4),]
names(df.means2)[names(df.means2) == 'V2'] <- 'State'
names(df.means2)[names(df.means2) == 'V4'] <- 'Proportion'
df.new <- cbind(df.means2$State,df.means2$Proportion)
knitr::kable(head(df.new),booktabs = TRUE, align = "c", caption = "Excerpt of dataset") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

And here Table \@ref(tab:tab3) gives the states with the highest obesity rates.

```{r tab3, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means3 <- df_means[order(df_means$V4, decreasing = T),]
names(df.means3)[names(df.means3) == 'V2'] <- 'State'
names(df.means3)[names(df.means3) == 'V4'] <- 'Proportion'
df.new2 <- cbind(df.means3$State,df.means3$Proportion)
knitr::kable(head(df.new2),booktabs = TRUE, align = "c", caption = "Excerpt of dataset") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

  From these tables and the chart above we see the lowest obesity rate in the United States is Colorado with 20.1% and the highest is Mississippi with 34.6%. For this analysis we want to see whether physical activity factors such as aerobic excercise. Below in \@ref(fig:fig2) however we will briefly see how these obesity rates have changed by the end of the decade.

```{r fig2, echo = FALSE, fig.cap = "Bar plot of Obesity by State", fig.width=8,fig.height=8}
### Bar plot of Obesity by State ###
df2 <- subset(df, Year == 2020)
df2 <- subset(df2, Question == "Percent of adults aged 18 years and older who have obesity")
df2 <- df2[order(df2$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df2[i,4],df2[i+1,4],df2[i+2,4],df2[i+3,4],df2[i+4,4],df2[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df_m <- cbind(unique(df2$Year),unique(df2$State), unique(df2$Question), round(x, digits = 1))
df_m <- as.data.frame(df_m)
df_l <- melt(df_m[order(df_m$V4),])
p <- ggplot(df_l, aes(x = V2, y = as.numeric(V4), fill = V4)) +scale_y_continuous(limits = c(0,50)) + theme(legend.position="none", axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=0)) + geom_bar(width = 0.8, stat = "identity", position = 'dodge') +
  xlab("State") +
  ylab("Percent of Population")

p + coord_flip()
```

We see from \@ref(fig:fig2) that the overall rate of obesity has clearly increased, however the states with the highest and lowest rates remain largely the same as we can see from Table \@ref(tab:tab4) and Table \@ref(tab:tab5) below.

```{r tab4, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means4 <- df_m[order(df_m$V4),]
names(df.means4)[names(df.means4) == 'V2'] <- 'State'
names(df.means4)[names(df.means4) == 'V4'] <- 'Proportion'
df.new4 <- cbind(df.means4$State,df.means4$Proportion)
knitr::kable(head(df.new4),booktabs = TRUE, align = "c", caption = "Excerpt of Chart 2") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

```{r tab5, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means5 <- df_m[order(df_m$V4, decreasing = T),]
names(df.means5)[names(df.means5) == 'V2'] <- 'State'
names(df.means5)[names(df.means5) == 'V4'] <- 'Proportion'
df.new5 <- cbind(df.means5$State,df.means5$Proportion)
knitr::kable(head(df.new5),booktabs = TRUE, align = "c", caption = "Excerpt of dataset") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

# Discussion {#Discussion}
